% !TEX root =thesis.tex
\section*{Acknowledgments}

First and foremost I'd like to thank my supervisor Brian Schmidt. He struck a balance between academic independence and supervision that allowed me to explore a lot of different fields of astronomy, but also focused me on the thesis when necessary. Brian did not only guide me professionally but also personally making him a true `Doktor Vater' (literally `doctor father' german name for a PhD supervisor). Thank you for five exciting, interesting and wonderful years here at Mt.~Stromlo and to many more years of fruitful collaboration and friendship in astronomy or otherwise.

I have to thank Rainer Wehrse (who unfortunatley passed away) without whom I would have never been able to start my PhD at Mt.~Stromlo.

My supervisory panel consisted of Mike Bessell, Frank Briggs, Bruno Leibundgut and Reynald Payne.
I thank Mike Bessell for many hours of chats about photometry and stellar spectroscopy. He has been a very patient teacher even in times when my questions were not posed all to well.  
I thank Frank Briggs for encouraging me to fearlessly ask questions about any subject in the many cosmlogy lunches that I was ignorant about. 
I thank both Bruno Leibundgut and Reynald Payne for being my external advisors. 

At Mt.~Stromlo there have been many people who made my stay fun, engaging and exciting. I will unfortunately only be able to name a few of them.
In the academic ranks, Harvey Butcher has certainly contributed to my pleasant stay at Mt.~Stromlo and I'd like to thank him for that. Not only through his financial support, but also through his advice on the \textsc{Dalek}~project. He suggested that nonlinear optimisation is a very active field and that my problem is not unique (which I had assumed). 
I have to thank Ken Freeman for his help in particular with the use of Fourier transforms to analyse spectra. 
Peter Wood has always been very helpful when concerning questions of stellar evolution and I thank him for his patience.
In the same spirit I thank Amanda Karakas who has taught me a lot stellar evolution and has tolerated the music and language next doors.
Stuart Sim has been of invaluable help in the the recent months, educating me about supernova radiative transfer and supernova theory as well as many chats over tea or coffee - thank you.
I have to thank Chris Onken for his unbreakable cheerful spirit throughout many projects that we have done together.
David Yong has been very patiently teaching me stellar abundance analysis - thank you.
I thank all the students at Mt.~Stromlo for their friendship and support over the last few years. Especially I'd like to thank Brad Tucker for his catering services for many Mt.~Stromlo events. 
Out of the Mt.~Stromlo crowd I have to thank, last but not least, my office mate Simon Murphy for his four years of a fun-filled and enjoyable PhD experience as well as his zealous love for Python that we both share.

Finally I have to thank the Computer Section. All of them have been very helpful, but I have to thank especially Kim and Bill for their computer support as well as witty remarks.

I have to thank all of my collaborators for their help and comments and especially Philipp Podsiadlowski for his valuable insights in binary star evolution and his patience in teaching me.
In addition I have to thank my collaborator James Montgomery for helping me with all things about Genetic algorithms.
I have to thank the MPA Supernova group for their hospitality and companionship during my stays with them. Specifically I'd like to thank Stephan Hachinger my collaborator, who has helped me master the spectrum synthesis code and patient in teaching me about the theory underlying that code.

I'd like to thank Thomas Magill for designing such a wonderful cover. His artistic skill also made the film `Starcatchers' a success.

Outside the astronomy community I have to thank all the people that contributed to the wonderful \textsc{Numpy}, \textsc{Scipy} and \textsc{Matplotlib} computing environment. I have to especially thank the support I have received from mailinglists of these products and the IRC \textsc{Python} chat room.

I have to thank all of my friends and family that have accompanied on this journey and helped when things seemed dire.

Last but not least I have to thank my parents Gertraud and Werner. Their unwaivering support, love and companionship have made it possible for me to reach this goal in life. 


%%% Local Variables:
%%% TeX-master: "thesis.tex"
%%% End:
