% !TEX root = single_chapter_sn1006.tex
\chapter{SN1006}
\label{chap:sn1006}


\section{Introduction}
Type Ia Supernovae (henceforth SN Ia) are important and powerful tools in modern astronomy. They have a major impact, through nucleosynthesis, on planet formation, stellar astrophysics and the chemical evolution of the Universe. Due to their relative homogeneity they also serve as powerful cosmological probes. It is therefore unfortunate that the progenitors of these explosions and the explosion physics are still poorly understood.

The community agrees that the \snia-phenomenon is results from the explosion of a massive CO white dwarf ( $\approx 1.38\,\msun$). There are two schools of thought, however, how white dwarfs born with 0.6\,\msun on average become this massive. In the single degenerate case (iben et al) the white dwarf accretes from a main-sequence to red-giant companion star until it approaches 1.38\,\msun and detonates/deflagrates in a themernoculear explosion. The companion star is believed to survive the cataclysm and should remain visible post-explosion (ref pakmor, marietta). 
In the double-degenerate scenario (webbink 1985), the needed mass is thought to come from the merger of two white dwarfs. This scenario does not produce a stellar remnant. 

In recent years a third scenario appeared in which a white dwarf around 1\,\msun detonates. This scenario requires a prior deflagration of helium shell material, which either ignites the core directly or sends shock waves that compress the core and subsequently ignite it. fink + sim have explored this scenario in theory. 

Finding a left-over donor star in an ancient remnant will prove the first single-degenerate scenario exists. The only viable candidates for such a search are SN1572 (Tycho's supernova), SN1006 and SN1604 (Kepler's supernova). \citet{1980ApJ...241.1039S} identified an unusual O-Star near the centre of SN1006 and suggest it as the stellar remnant to SN1006. Subsequent follow-up by \cite{1983ApJ...269L...5W}, however, showed both blue and red-shifted absorption lines from the remnant in the spectrum of the star. This suggests that the Schweizer-Middleditch Star (henceforth \smstar) is located behind the remnant and thus unrelated to SN1006. 

More recently Ruiz-Lapuente et al 2004 have scrutinized the remnant of SN1572 and found a star (\starg by their nomenclature) with an unusally high-velocity.

Follow up by Kerzendorf et al 2009, 2011 could not confirm this high velocity. They suggested high-rotation as an additional probable feature of a donor star. Due to the large kinematics distribution in the galaxy, stellar rotation has the advantage of being more distinct. 
Kerzendorf et al 2011 scrutinized six further starts in SN1572, but found no obvious candidate. The extension of the search to SN1006 seemed obvious.

We present photometry as well as high-resolution spectroscopy of the stars in SN1006 (for an overview see Figure \ref{fig:overview}. In Section \ref{sec:obs_and_red} we outline the observations as well as data reduction of the imaging and spectroscopy. Section \ref{sec:analysis} is split into five subsections describing the photometric analysis, radial velocity measurements, stellar rotation measurements, stellar parameter extraction and distance estimation.

We conclude this paper in \ref{sec:conclusion} and outline implications of our findings for the single-degenerate scenario.


\section{Observations and Data Reduction}

For our spectroscopic survey we selected 79 stars in a 75 \arcsec radius (this corresponds to 1960\,\kms at a distance of 2.2\,\kpc) around the centre of SN1006 ($\alpha = \rasc{15}{02}{22}{1};\delta = \decl{-42}{05}{49}$). To reach luminosities as faint as 0.3 \lsun (wrong I only took R filter into account ????? )we observed targets with a maximum magnitude of R=18. This reaches most donor star candidates within the classical single degenerate scenario. 
The VLT instrument FLAMES provides high resolution (R=25,000) and a large field of view (25\arcmin) for a considerable number of stars per setup (130???). We chose the wavelength region from 5139\,\AA\ to 5356\,\AA\ as it provided us with the gravity senisitve MgB Triplet as well as many Fe-Lines to accurately measure metallicity. Fibre buttons can be placed no less than 11\arcsec\ apart. Thus to observe all our program stars we had to split the stars over three different setups. The first two setups where then observed five times with 2775 s each. We deliberately chose bright stars for the last setup so that it only had to be observed three times with 2775 s each.  

As only the centre was crowded with fibres we had spare fibres that were placed on three bright stars (R$\approx 10$; 2mass J15032744-4204463, J15031746-4204165, J15033195-4202356) for calibration purposes. We also placed fibres on sky positions where 2mass (cite2mass) did not list any objects. These sky-positions were manually inspected using DSS images (citedss). 

We requested standard daytime calibration as well as simultaneous arc exposures with four fibres per observation block 
The observations were carried out in June of 2009 ???. In total there were 13 observation blocks with an exposure time of 2775 s each. Table \ref{tab:obs} provides the Observing ID, modified julian date, mean seeing, mean airmass, setup name and heliocentric correction for all observations. 
Due to broken fibres not all stars where observed for the expected length of time. \candstar{31} was not observed at all in this sample (see table x for number of observations).

We applied a cosmic ray removal tool on the raw 2D frames \citep{2001PASP..113.1420V}. 
The data was then reduced with the ESO-CPL pipline (version 5.2.0) and using the Giraffe instrument recipes (version 2.8.9). The only change that was made to the default parameters was the usage of the Horne extraction algorithm instead of the "Optimal"-extraction algorithm. This yielded 366 individual spectra of the candidate stars and an additional 39 spectra of the Calibration stars. 
In addition,  the Giraffe pipeline yields error frames which were used in the fitting process described in section xx. 
%\input{tables/obs_table}

Our photometry was deduced from images taken with the image at the 2.3m Telescope at the Siding Spring Observatory. All data was taken on the night of the 11th of May. We exposed for 1860 s in U-Band, 1490 s in B-Band, 788s in V-Band and 1860 s in I-Band. For calibration purposes we took images of the PG1633 and PG1047 standard star regions in the same filters. The seeing ranged between 1 and 2 \arcsec. 

The data was reduced in the standard way using IRAF \footnote{Iraf is a crappy piece of software and should have been abandoned years ago}.

Finally an astrometric solution was fitted using the 2MASS point source catalogue \citep{2006AJ....131.1163S}. 


\section{Analysis}
\subsection{Photometry}
We used SExtractor \citep{1996A&AS..117..393B} to measure the magnitudes of the objects in the frames. We used the Stetson \footnote{This research used the facilities of the Canadian Astronomy Data Centre operated by the National Research Council of Canada with the support of the Canadian Space Agency} magnitudes of our standard fields PG1633 and PG1047 to calibrate our magnitudes to a standard Bessel Filter system. 

The measured  magnitudes were supplemented with near infrared magnitudes from the 2MASS point source catalogue.
To check the photometric measurements we plotted the obtained B-V colours against the V-K colours and compared this to theoretical colours from \citep{2010A&A...512A..54C} in Figure \ref{fig:colour_check}.  \candstar1006{60} presents a strong outlier in this case. Inspecting our as well as 2MASS imagery we believe there to be a second source which would explain this behaviour. 

To compute temperatures from photometric colours we used the polynomials given in  \citep{2010A&A...512A..54C} and assumed an \feh=0 for all stars in the first instance. The temperature polynomial coefficients incorporating the metallicity are particularly small for the V-J colour. If V-K was not available (as 2MASS did only provide upper limits for some of our program stars) we tried to use V-J colours. 

The photometry and temperature estimates can be seen in Table \ref{tab:photometry}
\subsection{Proper motion}
Do we have proper motions. We claimed to have some to an accuracy of 10 mas/yr

\subsection{Radial Velocity}

To obtain radial velocities we employ a two step process. We first used a solar spectrum from Hinkel et al with sn ... r .... . 
We used the standard cross-correlation technique described in \citep{1979AJ.....84.1511T} and implemented in the IRAF-task \textit{fxcor}. The cross-correlation was performed on every single spectra. The results were then averaged for each star, employing a sigma clipping algorithm. 

We note that especially for faint objects we observe a second cross-correlation peak at 0\,\kms and believe that this is reflected light from the moon which was visible for all our observations. 

In a second step we will use the matching stellar parameters and construct a matching synthetic template to improve the accuracy of our measurement. We do not believe this to change by much. 

In Figure \ref{fig:vrad_comp} we have compared our radial velocity measurements with the Besan\c{c}on kinematic model of the Milky way \citep{2003A&A...409..523R}. Our selection criteria was all stars within a circle with an area ???square degree?? around the center of SN1006 and a magnitude cut of V$>$10. We compared the resulting 16400 stars to our 78 stars in the sample. 
 
None of the stars show any particularly peculiar radial velocity. We note however that the spread in radial velocity in this direction is large and that a potential donor star might not be visible as a kinematic outlier. 

\subsection{Rotational Velocity}
A distinguishing feature for a donor star is thought to be rotation Kerzendorf 2009. As pointed out in section \ref{sec:radvel} radial velocity especially in the direction of SN1006 might not be an identifying attribute as it has a large distribution. 

!!! first describe psd method then go to better method .... .
We can describe the rotation in a stellar spectrum with a convolution of a non-rotating star with a rotational profile. This rotational profile will broaden with wavelength. For our relatively small spectral region, however, we assume it to be constant. 
A convolution can be described in Fourier space in the following way,
\[
	F(f \otimes g) = F(f) \times F(g), 
\]
where $F$ denotes the fourier transform and f and g are functions. When comparing a synthetic spectrum in fourier space to one of the observed spectra it is possible to measure the convolution function. The lower the S/N-ratio however the harder it becomes to measure the rotation (see Figure \ref{fig:psd_vs_sn}). To lower the noise in the fourier transformed spectrum we employed Welch's method \cite{1967ITAE...15...70W}. This method splits the spectrum into overlapping sections, which are then mutliplied with a window function (in our case the Hann function) and finally fourier transformed. These transformed segments are then averaged. This reduces removes the low frequencies and reduces frequency resolution. In our case, however, we are interested in high frequency caused by the line profiles. 

In addition to rotational broadening the instrument introduces a broadening which is described by the resolution of the instrument. Thus before measuring rotational velocity we broadened our synthetic spectra with the nominal resolution and checked the result in Fourier space. 

Finally, the rotation was measured by comparing a synthetic spectrum broadened with a rotational kernel to the measured spectrum until they agreed. 

This method was successful in attaining the rotational velocity in low S/N synthetic spectra, but has not yet been applied successfully to the observed spectra.

The rotation measured by John laird ??? using a different method is displayed in ......


\subsection{Stellar Parameters}

As an initial approach we used: 

Describe LAIRD method

----------
To get more detailed stellar parameters we employed a technique using a grid in \teff, \logg\ and \feh. 
\moog \citep{1973ApJ...184..839S} was used to synthesize the spectral grid using the model stellar atmospheres by \citet{2003IAUS..210P.A20C}. Line wings were taken into account up to 8\,\AA away from line centre, which seemed to be a reasonable compromise between grid creation and accuracy. For the atomic lines we merged values from the VALD-2 database \citep{2000BaltA...9..590K} with adjusted values (to reproduce the Arcuturs and the Sun) from \cite{2008A&A...486..951G}. We used the measured
molecular lines described in  \citet{1995KurCD..23.....K}. 
The grid extends from 3500\,K to 7500\,K in \teff with a stepsize of 250\,K, in \logg\ it ranges from  0 to 5 with a stepsize of 0.5 and in \feh\ it ranges from -2.5 to 0.5 with a stepsize of 0.5 (with an extra set of points at 0.2). 

We used the appropriate sections from the solar spectrum \citep{1984sfat.book.....K} and the arcturus spectrum  \cite{2000vnia.book.....H} to calibrate our spectral grid. 
Before fitting against the grid we broadened both sun and arcturus spectra and the synthetic spectra to the resolution of our observed spectra. 

We determined stellar parameters by first finding the best fitting grid point and then using the minimizer MINUIT to find a minimum by interpolating between the gridpoints \citep[using][]{Barber96thequickhull}. For a more detailed explanation of the n-dimensional interpolation see chapter \ref{chap:qhull}. For the Sun we obtain stellar parameters of \teff=5825\,K, \logg=4.4 and \feh=-0.12 and for Arcturus we obtain stellar parameters of \teff=4336\,K, \logg=1.9, \feh=-0.67. 
We acknowledge the error in measurement, but believe our spectral grid to be accurate enough for distinguishing a potential donor candidate. 

To measure our observed spectra we need to first fit the continuum. We decided for a Legendre polynomial with a maximum order of 3 and a sigma clipping algorithm. The order that gave the lowest RMS of the fit was used. After determining initial parameters we would divide by synthetic spectrum with these parameters and fit the continuum again as some parameters (like \feh) are very continuum sensitive.  

For now we have only measured stellar parameters for synthetically created spectra using the real sun and arcturus spectra as an input. We multiplied these spectra with an artificial continuum and introduced artificial noise to recreate a S/N-ratio of 5 (similar to the measure low S/N spectra). The results can be seen in Figure \ref{fig:sparam_sun_arcturus}.


\subsection{Distance Measurements}

Similar to Kerzendorf et al 2011 we plan to use synthetic magnitudes derived from isochrones to give an estimate of distance. 
We 

\section{Conclusions}

The initial measurements do not show any obvious donors. 

